---
title: "visualv2"
author: '1'
date: "2021/5/8"
output: html_document
---


---
title: "Untitled"
author: '1'
date: "2021/5/8"
output: html_document
---

```{r}
datasetbegin =read.csv("C:/Users/pc/Desktop/527/googleplaystore.csv",header = T, encoding = 'UTF-8')
dim(datasetbegin)
dataset = na.omit(datasetbegin)
Sys.setlocale("LC_TIME","C")
dataset$Last.Updated = as.Date(dataset$Last.Updated,format = "%B %d, %Y")
#fix(dataset)
dataset$add_years = unclass(as.POSIXlt(dataset$Last.Updated))$year + 1900
dataset$add_month = unclass(as.POSIXlt(dataset$Last.Updated))$mon + 1
```


```{r}
dataset = subset(dataset,select = -c(Price,Genres,Last.Updated,Current.Ver))
dim(dataset)
dataset = na.omit(dataset)
```

```{r}
library(tidyr)
dataset = separate(dataset, Installs, into = c("Installsnew"),sep = "\\+")
attach(dataset)
Installsnew = gsub(",","",Installsnew)
Installsnew = as.numeric(Installsnew)
dataset$Installsnew = Installsnew
```

```{r}
library(tidyverse) 
library(data.table)
library(ggplot2)
dataset %>% filter(dataset$Category != "") %>% group_by(Category) %>% dplyr::summarise(rating = mean(Rating,na.rm = TRUE)) %>% mutate(Category = reorder(Category,rating)) %>% ggplot()+
geom_bar(aes(Category,rating),stat = "identity",fill = "#01a2d9",alpha = 0.5, width = 0.4)+
coord_flip()+
  scale_y_continuous(breaks = seq(0,4.5,0.5),expand = c(0,0))+
  theme(plot.title = element_text(hjust = 0.5,size = 15))+
  ggtitle("Rating by Category")+
  ylab("Rating")+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.text.y = element_text(color = "black",size =10,hjust = 1),
        axis.ticks.length.x = unit(0.5,"lines"),
        axis.title = element_text(size = 12),
        panel.background = element_rect(fill = "white"))
```

```{r}
dataset = na.omit(dataset)
dataset %>%
  filter(dataset$Category!= "") %>%
  group_by(Category) %>%
  dplyr::summarise(Totalinstalls = sum(Installsnew,na.rm = TRUE)) %>%
  mutate(Category = reorder(Category,Totalinstalls))%>%
  mutate(Totalinstalls = Totalinstalls / 1000000) %>%
  ggplot()+
  theme_bw()+
  ggtitle("Categories with number of installs")+
  geom_point(aes(Category,Totalinstalls,color = Category,size = Totalinstalls),alpha = 0.4)+
  scale_size_continuous(range = c(4,10))+
  scale_y_continuous(limits = c(0,40000))+
  ylab("Total Installs (Million)")+
  theme(
    axis.text.x = element_text(angle = 45,hjust = 0.95),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
    panel.border = element_rect(color = "white"),
  )
```




```{r}
green_color <- "#69b3a2"
dataset$Reviews = as.numeric(dataset$Reviews)
dataset %>%
  filter(dataset$Category!= "") %>%
  group_by(Category) %>%
  dplyr::summarise(Mean_reviews = mean(Reviews,na.rm = TRUE)) %>%
  mutate(Category = reorder(Category,Mean_reviews))%>%
  ggplot(aes(x = Mean_reviews,y = Category),alpha = 0.4) + 
  geom_col(fill=green_color,alpha=0.8) +
  coord_flip() +
  labs(x="Mean of reviews",y="Category")+
  ggtitle("Mean reviews by Categories")+
   theme(
    axis.text.x = element_text(angle = 45,hjust = 0.95),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
  )
```


```{r}
dataset %>%
  filter(dataset$Category!= "") %>%
  group_by(Category) %>%
  dplyr::summarise(Mean_reviewsinstall_rate = mean(Reviews/Installsnew,na.rm = TRUE)) %>%
  mutate(Category = reorder(Category,Mean_reviewsinstall_rate ))%>%
  ggplot(aes(x = Mean_reviewsinstall_rate ,y = Category),alpha = 0.4) + 
  geom_col(fill="#69b3a2",alpha=0.8) +
  coord_flip() +
  labs(x="Mean of reviews/installnew rate",y="Category")+
  ggtitle("Mean reviews/installnew rate by Categories")+
   theme(
    axis.text.x = element_text(angle = 45,hjust = 0.95),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
  )
```


```{r}
dataset <- dataset %>% mutate(Reviews_installrate = Reviews/Installsnew)
plot(dataset$Reviews_installrate)
#installnew <500 miss
```

```{r}
df <- dataset %>% mutate(Reviews_installrate = Reviews/Installsnew) %>% filter(Installsnew >=10000)
```

```{r}
df %>%ggplot()+
  theme_bw()+
  ggtitle("Rating with Reviews/Installs rate")+
  geom_point(aes(Reviews_installrate,Rating),color = "#69b3a2",alpha = 0.4)+
  #scale_size_continuous(range = c(4,10))+
 # scale_y_continuous(limits = c(0,40000))+
  ylab("Ratings")+
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
    panel.border = element_rect(color = "white")
  )
```

```{r}
df %>% filter(Category == "GAME")%>%
  ggplot()+
  theme_bw()+
  ggtitle("Rating with Reviews rate(GAME)")+
  geom_point(aes(Reviews_installrate,Rating),color = "#69b3a2",alpha = 0.4)+
  geom_point(aes(x = 0.4489172, y = 4.6,stroke = 2),shape = 1, color="#CC0000", size=2.5)+  geom_label(label='	Clash of Clans',x = 0.43, y = 4.4,color='black', alpha= 0.5) +
  #scale_size_continuous(range = c(4,10))+
 # scale_y_continuous(limits = c(0,40000))+
  ylab("Ratings")+
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    panel.border = element_rect(color = "white")
  )
```
#instogram/ Facebookd
```{r}
df %>% filter(Category == "SOCIAL" & Reviews_installrate <=0.1)%>%
  ggplot()+
  theme_bw()+
  ggtitle("Rating with Reviews/Installs rate(SOCIAL)")+
  geom_point(aes(Reviews_installrate,Rating),color = "#69b3a2",alpha = 0.4)+
  geom_point(aes(x = 0.06657731, y = 4.5,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Instagram',x = 0.07, y = 4.35,color='black', alpha= 0.5)+ 
  geom_point(aes(x = 0.07812821, y = 4.1,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Facebook',x = 0.075, y = 3.95,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.034029574, y = 4.0,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Snapchat',x = 0.035, y = 4.15,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.004831125, y = 4.2,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Google',x = 0.0051, y = 4.05,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.017212518, y = 4.3,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Facebook lite',x = 0.019, y = 4.45,color='black', alpha= 0.5)+
  #scale_size_continuous(range = c(4,10))+
 # scale_y_continuous(limits = c(0,40000))+
  ylab("Ratings")+
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
    panel.border = element_rect(color = "white")
    )
```

```{r}
df %>% filter(Category == "SOCIAL" & Reviews_installrate <=0.1 & Size == "Varies with device" & Installsnew > 2e+8)%>%
  ggplot()+
  theme_bw()+
  ggtitle("Rating with Reviews rate(SOCIAL)")+
  geom_point(aes(Reviews_installrate,Rating),color = "#69b3a2",alpha = 0.4)+
  geom_point(aes(x = 0.06657731, y = 4.5,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Instagram',x = 0.07, y = 4.45,color='black', alpha= 0.5)+ 
  geom_point(aes(x = 0.07812821, y = 4.1,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Facebook',x = 0.075, y = 4.15,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.034029574, y = 4.0,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
   geom_label(label='Snapchat',x = 0.035, y = 4.05,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.004831125, y = 4.2,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
   geom_label(label='Google',x = 0.01, y = 4.15,color='black', alpha= 0.5)+
  geom_point(aes(x = 0.017212518, y = 4.3,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_label(label='Facebook lite',x = 0.019, y = 4.25,color='black', alpha= 0.5)+
  #scale_size_continuous(range = c(4,10))+
 # scale_y_continuous(limits = c(0,40000))+
  ylab("Ratings")+
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
    panel.border = element_rect(color = "white")
    )
```





```{r}
df %>% filter(Category == "COMMUNICATION")%>%
  ggplot()+
  theme_bw()+
  ggtitle("Rating with Reviews rate(Communication)")+
  geom_point(aes(Reviews_installrate,Rating),color = "#69b3a2",alpha = 0.4)+
  geom_point(aes(x = 0.1284286, y = 4.3,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  geom_point(aes(x =0.2374680, y = 4.8,stroke = 2),shape = 1, color="#CC0000", size=2.5)+
  #scale_size_continuous(range = c(4,10))+
 # scale_y_continuous(limits = c(0,40000))+
  ylab("Ratings")+
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    panel.border = element_rect(color = "white")
  )
```

#dummy variable
```{r}
dataset$Content.Rating[dataset$Content.Rating == "Everyone 10+"] <- "Everyone_10"
dataset$Content.Rating[dataset$Content.Rating == "Mature 17+"] <- "Mature_17"
dataset$Content.Rating[dataset$Content.Rating == "Adults only 18+"] <- "Adults_only_18"

```

```{r}
library(fastDummies)
data  = dummy_cols(dataset, select_columns = c("Category", "Content.Rating"),remove_first_dummy = TRUE)
```
#charcater varit
```{r}
data = subset(data, select = -c(Category, Content.Rating))
data$Type[dataset$Type == "Free"] = 0
data$Type[dataset$Type == "Paid"] = 1
#delete varies with device 
#table(dataset$Sizenew)
library(tidyr)
data = separate(data, Size,into = c("Sizenew"),sep = "M")
data = data[!data$Sizenew == "Varies with device",]

```

```{r}

dataset1 = separate(data, Sizenew, into = c("Sizenew1"),sep = "k")
k.index = which(data$Sizenew != dataset1$Sizenew1)
dataset1$Sizenew1 = as.numeric(dataset1$Sizenew1)
for (i in k.index){
  dataset1$Sizenew1[i] = (dataset1$Sizenew1[i]/1024)
}
data$Sizenew = dataset1$Sizenew1
```

```{r}
data$Android.Ver = substr(data$Android.Ver, 1,3)
data= data[!data$Android.Ver == "Var",]
data$Android.Ver = as.numeric(data$Android.Ver)
data$Type = as.numeric(data$Type)
data = na.omit(data)
```

```{r}
data = data%>% filter(data$Installsnew >= 1000)
data = data %>% mutate(Rating_install_target = data$Rating*data$Reviews_installrate)
data = subset(data, select = -c(App,Rating,Reviews,Installsnew,add_years,Reviews_installrate))
```
#outlier detection 
```{r}
library(OutlierDetection)
library(OutliersO3)
library(outliers)
a = nn(data,k=4)
for (i in a[2]){
  data = data[-i,]
}
```
#normalized 1:4 conclumn
```{r}
tmp = rep(0,4)
for (i in 1:4){
  tmp[i] = max(data[,i])
  data[,i] = data[,i]/tmp[i]
}
```
# delete content.rating.unrated 
```{r}
data = subset(data, select = -c(Content.Rating_Unrated))
```

```{r}
summary(data)
lm.fit = lm(data$Rating_install_target~., data = data)
summary(lm.fit)
```
# plot rating_install target 
```{r}
library(ggplot2)
data %>% ggplot(aes(x=Rating_install_target)) + geom_histogram(color="black", fill="lightblue")+
  theme(legend.position="none")
```
#Spilt the dataset
```{r}
set.seed(13)
train = sample(nrow(data),0.6*nrow(data))
data.Train = data[train,]
data.testX=data[-train,"Rating_install_target"]
```

#knn
# ```{r}
# set.seed(133)
# Train = data[train,]
# Test=data[-train,]
# y_train=Train["Rating_install_target"]
# y_test=Test["Rating_install_target"]
# dim(Train)
# dim(Test)
# X_train=Train[,1:41]
# X_test=Test[,1:41]
# ```

# ```{r}
# Train_X_min=min(X_train)
# Train_X_max=max(X_train)
# newTrain_X=(X_train- Train_X_min)/(Train_X_max - Train_X_min)
# Test_X_min=min(X_test)
# Test_X_max=max(X_test)
# newTest_X=(X_test- Test_X_min)/(Test_X_max - Test_X_min)
# ```
# 
# ```{r}
# library(class)
# set.seed(1)
# test_error= rep(0,20)
# for (K in 1:20){
# knn.pred = knn(train = newTrain_X,	
#                test = newTest_X,	
#                 cl = y_train[,1],	
#                 k =K) 
# knn.pred=as.numeric(as.character(knn.pred))
# test_error[K] = mean((knn.pred-y_test[,1])^2)^0.5
# }
# test_error
# plot(c(1:20),test_error, type = "b")
# ```
# 
# ```{r}
# set.seed(1)
# knn.pred = knn(train = newTrain_X,	
#                test = newTest_X,	
#                 cl = y_train[,1],
#                 k =2) 
# knn.pred=as.numeric(as.character(knn.pred))
# px=c(1:20)
# y1=knn.pred[0:20]
# y2=y_train[,1][0:20]
# plot(px,y1,col=2,type="b",xlab = "different apps",ylab ="predic y vs test y")
# lines(px,y2,col=3,type="b")
# legend("topright",legend=c("y_predict","y_test"),pch=c(20,20),col=c(2,3))
# 
# ```



#xgboost

```{r}
library(xgboost)
set.seed(1)
RMSE_train = rep(0,20)
RMSE_validation = rep(0,20)
RMSE_test = rep(0,20)
eta_variable = seq(0.1,0.29,by = 0.01)
#max_depth_variable = seq(1,10, by = 1)
#subsample_varibale = seq(0.5,1,by = 0.1)
for (i in 1:20){
 xgbcv = xgb.cv(data = data.matrix(data.Train[,-41]), 
 label = data.Train$Rating_install_target, 
 eta = eta_variable[i],
 max_depth = 8, 
 nround = 30, 
 subsample = 1,
 nfold=5,
 early_stopping_rounds = 3,
objective = "reg:squarederror",
)
RMSE_train[i] = min(xgbcv$evaluation_log$train_rmse_mean)
RMSE_validation[i] = min(xgbcv$evaluation_log$test_rmse_mean)
xgb = xgboost(data = data.matrix(data.Train[,-41]), 
 label = data.Train$Rating_install_target, 
 eta = eta_variable[i],
 max_depth = 8, 
 nround = 30, 
 subsample = 1,
 early_stopping_rounds = 3,
objective = "reg:squarederror",
)
datamodel_xgboost = predict(xgb, newdata = data.matrix(data[-train,-41]))
RMSE_test[i] = mean((datamodel_xgboost -data.testX)^2)^0.5
}
plot(eta_variable ,RMSE_test, xlab = "eta", ylab = "RMSE",type = "b")
```




#tunning parameter 
```{r}
library(xgboost)
set.seed(1)
xgb = xgboost(data = data.matrix(data.Train[,-41]), 
 label = data.Train$Rating_install_target, 
 eta = 0.2,
 max_depth = 8, 
 nround = 30, 
 subsample = 1,
 early_stopping_rounds = 3,
objective = "reg:squarederror",
)
names = dimnames(data.matrix(data.Train[,-41]))[[2]]
importance_matrix = xgb.importance(names, model = xgb)
xgb.plot.importance(importance_matrix[1:20,], col = green_color)
datamodel_xgboost = predict(xgb, newdata = data.matrix(data[-train,-41]))
mean((datamodel_xgboost -data.testX)^2)^0.5
```

```{r}
Target_hat = predict(xgb, newdata = data.matrix(data[train,-41]))
data_s = data.frame(data[train,],Target_hat)
data_s$Sizenew_raw = data_s$Sizenew*100
data_s$Type_raw = data_s$Type*1
data_s$Android.Ver_raw = data_s$Android.Ver*8
data_s$add_month_raw = data_s$add_month*12
```

#transfer dummy variables into the category
```{r}
data_s <- data_s %>% 
  mutate(Content.Rating_Adults_only_18 = ifelse((Content.Rating_Everyone + Content.Rating_Everyone_10 + Content.Rating_Mature_17 + Content.Rating_Teen) == 0 , 1, 0)) 
attach(data_s)
data_s <- data_s %>% 
  mutate(Category_ART_AND_DESIGN = ifelse((Category_AUTO_AND_VEHICLES + Category_BEAUTY + Category_BOOKS_AND_REFERENCE + Category_BUSINESS + Category_COMICS +
Category_COMMUNICATION +Category_DATING+Category_EDUCATION+          
Category_ENTERTAINMENT+Category_EVENTS+Category_FAMILY+             
Category_FINANCE+Category_FOOD_AND_DRINK+Category_GAME+               
Category_HEALTH_AND_FITNESS+  Category_HOUSE_AND_HOME     +Category_LIBRARIES_AND_DEMO +
Category_LIFESTYLE          +Category_MAPS_AND_NAVIGATION+Category_MEDICAL            +
Category_NEWS_AND_MAGAZINES +Category_PARENTING          +Category_PERSONALIZATION    +
Category_PHOTOGRAPHY        +Category_PRODUCTIVITY       +Category_SHOPPING           +
Category_SOCIAL             +Category_SPORTS             +Category_TOOLS              +
Category_TRAVEL_AND_LOCAL   +Category_VIDEO_PLAYERS      +Category_WEATHER) == 0 , 1, 0)) 


# function to reconstruct from dummy
catmaker <- function(data, varnames, catname) {

  data[,catname] <- apply(data[,varnames], 1, function(i) varnames[which(i == 1)])

  return(data)

}
data_s <- catmaker(data =data_s, varnames = c("Content.Rating_Everyone","Content.Rating_Everyone_10",    "Content.Rating_Mature_17","Content.Rating_Teen","Content.Rating_Adults_only_18"), catname = "Content.Rating_raw")
data_s <- catmaker(data=data_s, varnames = c("Category_ART_AND_DESIGN","Category_AUTO_AND_VEHICLES","Category_BEAUTY", "Category_BOOKS_AND_REFERENCE" ,"Category_BUSINESS" ,            "Category_COMICS"              
,"Category_COMMUNICATION"  ,      "Category_DATING",               "Category_EDUCATION"           
,"Category_ENTERTAINMENT"   ,     "Category_EVENTS" ,              "Category_FAMILY"              
,"Category_FINANCE"    ,   "Category_FOOD_AND_DRINK" ,      "Category_GAME"                
,"Category_HEALTH_AND_FITNESS",   "Category_HOUSE_AND_HOME",       "Category_LIBRARIES_AND_DEMO"  
,"Category_LIFESTYLE" ,           "Category_MAPS_AND_NAVIGATION",  "Category_MEDICAL"             
,"Category_NEWS_AND_MAGAZINES",   "Category_PARENTING",            "Category_PERSONALIZATION"     
,"Category_PHOTOGRAPHY",          "Category_PRODUCTIVITY",         "Category_SHOPPING"            
,"Category_SOCIAL",         "Category_SPORTS",               "Category_TOOLS"               
,"Category_TRAVEL_AND_LOCAL",     "Category_VIDEO_PLAYERS",        "Category_WEATHER" ), catname = "Category")

data_s$Content.Rating_raw_cleaned <- stringr::str_remove(data_s$Content.Rating_raw, "Content.Rating_")
data_s$Category_raw_cleaned <- stringr::str_remove(data_s$Category, "Category_")
```
#plot the type with Target_value 
```{r}
yhat_p0 <- ggplot(data_s, aes(x=as.factor(Type), y=Target_hat)) + 
  geom_boxplot(fill=green_color)  +  
  coord_cartesian(ylim=c(0, 1)) + 
  stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed",color = "red")+
  labs(x="Type",y="Target value")+
  ggtitle("Type  with Target value(Free vs Paid)")+
   theme(
    axis.text.x = element_text(hjust = 0.5,size =12,vjust=3),
    axis.title.x=element_text(vjust=3,  size=15), 
    axis.title.y=element_text(size=15), 
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
yhat_p0
```
#plot Content Rating with Target value
```{r}
yhat_p <- ggplot(data_s, aes(x=Content.Rating_raw_cleaned, y=Target_hat)) + 
  geom_boxplot(fill=green_color)  +  
  coord_cartesian(ylim=c(0, 1)) + 
  stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed",color = "red")+
  labs(x="Content Rating",y="Target value")+
  ggtitle("Content Rating with Target value")+
   theme(
    axis.text.x = element_text(hjust = 0.5,size =12,vjust=3),
    axis.title.x=element_text(vjust=3,  size=15), 
    axis.title.y=element_text(size=15), 
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
yhat_p
```

```{r}
yhat_p2 <- ggplot(data_s, aes(x=Category_raw_cleaned, y=Target_hat)) + 
  geom_boxplot(fill=green_color) +  
  coord_cartesian(ylim=c(0, 1)) + 
  stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed", color = "red")+
  labs(x="Category",y="Y_hat(Target_value)")+
  ggtitle("Categories with Y_hat(Target_value)")+
   theme(
    axis.text.x = element_text(angle = 45,hjust = 0.95),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
  )
yhat_p2
```
#plot category the target value 
```{r}
data_s %>% group_by(Category_raw_cleaned) %>% summarise(mean_yhat = mean(Target_hat))%>% mutate(Category_raw_cleaned = reorder(Category_raw_cleaned,mean_yhat)) %>% ungroup() %>%
  ggplot() + 
  geom_point(aes(x=as.factor(Category_raw_cleaned), y=mean_yhat,color = Category_raw_cleaned,size = mean_yhat),alpha = 0.4) + 
  geom_line(aes(x=as.factor(Category_raw_cleaned), y=mean_yhat), color = green_color)+
    labs(x="Category",y="Target value")+
  ggtitle("Categories with Target value")+
   theme(
    axis.text.x = element_text(angle = 45,hjust = 0.95),
    legend.position = "none",
    axis.title.x=element_text(vjust=3,  size=15), 
    axis.title.y=element_text(size=15), 
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
```
#plot top 5 category the target value 
```{r}
data_s %>% filter(Category_raw_cleaned %in% c("WEATHER","GAME","SOCIAL","SPORTS","FAMILY","EDUCATION")) %>% 
  ggplot(aes(x=as.factor(Category_raw_cleaned), y=Target_hat)) + 
  geom_boxplot(fill=green_color) +  
  coord_cartesian(ylim=c(0, 1)) + 
  stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed", color = "red")+
  labs(x="Category",y="Target value")+
  ggtitle("Categories with Target value")+
  theme(
    axis.text.x = element_text(hjust = 0.5),
    legend.position = "none",
    axis.title.x=element_text(vjust=1,  size=15), 
    axis.title.y=element_text(size=15), 
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
```

# ```{r}
# x<- data.matrix(subset(data.Train, select = -Rating_install_target))
# pdp_plot <- partial(xgb, pred.var = "Sizenew", ice=FALSE, center = TRUE, plot = TRUE, rug = TRUE, alpha=0.1, plot.engine = "ggplot2", train = x,type = "regression")
# pdp_plot
# ```

# ```{r}
# yhat_p2 <- ggpoint(data_s, aes(x=as.factor(add_month_raw), y=Target_hat)) + 
#   geom_boxplot(fill=green_color) +  
#   coord_cartesian(ylim=c(0, 1)) + 
#   stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
#                  width = .75, linetype = "dashed")
# yhat_p2
# ```

# plot month with Target_value
```{r}
data_s %>% group_by(add_month_raw) %>% summarise(mean_yhat = mean(Target_hat)) %>% ungroup() %>%
  ggplot() +  labs(x="Month",y="Target_value")+
  geom_point(aes(x=as.factor(add_month_raw), y=mean_yhat)) + 
  geom_line(aes(x=add_month_raw, y=mean_yhat), color = green_color)+
  ggtitle("Month with Target_value")+
   theme(
    axis.text.x = element_text(hjust = 0.5,size =12,vjust=3),
    axis.title.x=element_text(vjust=3,  size=15), 
    axis.title.y=element_text(size=15), 
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
```

```{r}
data_s %>% 
group_by(Sizenew_raw) %>% summarise(mean_yhat = mean(Target_hat)) %>% ungroup() %>%
  ggplot() +  labs(x="Size",y="Target_value")+
  coord_cartesian(ylim=c(0, 0.8))+ 
  geom_point(aes(x=Sizenew_raw, y=mean_yhat)) + 
  ggtitle("Size with Target_value")+
   theme(
    axis.text.x = element_text(hjust = 0.5,size =12,vjust=3),
    axis.title.x=element_text(vjust=3,  size=15), 
    axis.title.y=element_text(size=15), 
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 10)),
  )
```

```{r}
data_s %>% mutate(Android.Ver_raw = as.character(Android.Ver_raw)) %>%
  ggplot(aes(x=Android.Ver_raw, y=Target_hat)) +  labs(x="Andro",y="Y_hat(Target_value)")+
  #geom_point(aes(x=data_s$Android.Ver_raw, y=Target_hat)) + 
  geom_boxplot(fill=green_color)+
  ggtitle("Android.Ver with Y_hat(Target_value)")+
  stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),width = .75, linetype = "dashed", color = "red")+
   theme(
    axis.text.x = element_text(hjust = 0.95),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5,margin = margin(b = 20)),
  )+ coord_cartesian(ylim=c(0, 0.5)) 


```
```

#SVM
# ```{r}
# library(e1071)
# rate.fit.svm = svm(Rating_install_target~., data = data.Train , kernel ="radial", gamma = 0.01, cost = 2.511886)
# mean((rate.fit.svm$residuals)^2)^0.5
# datamodel_ratehatsvm = predict(rate.fit.svm, newdata = data[-train,])
# mean((datamodel_ratehatsvm-data.testX)^2)^0.5
# ```




# ```{r}
# tune.out = tune(svm, Rating_install_target~., data = data.Train ,kernel ="radial", gamma =10, ranges = list(cost = 10^seq(-2, 1, by = 0.2)), tunecontrol = tune.control(cross= 5))
# summary(tune.out)
# ```
# ```{r}
# a  = summary(tune.out)
# a$performances
# 
# ```{r}
# library(e1071)
# rate.fit.svm = svm(Rating_install_target~., data = data.Train , kernel ="sigmoid", gamma = 0.001, cost = 2.511886)
# mean((rate.fit.svm$residuals)^2)^0.5
# datamodel_ratehatsvm = predict(rate.fit.svm, newdata = data[-train,])
# mean((datamodel_ratehatsvm-data.testX)^2)^0.5
# ```
# ```{r}
# library(randomForest)
# set.seed(1)
# train.errors.randomforest = rep(0, 10)
# test.errors.randomforest  = rep(0, 10)
#  for (i in 1:10){
# rate.fit.randomforest = randomForest(Rating_install_target~., data = data.Train,mtry= 2*i,ntree =1000, importance=TRUE)
# train.errors.randomforest[i] =(mean((rate.fit.randomforest$predicted-rate.fit.randomforest$y)^2))^0.5
#  data_ratehat = predict(rate.fit.randomforest, newdata = data[-train,])
#  test.errors.randomforest[i] =  mean((data_ratehat-data.testX)^2)^0.5
# }
# plot(c(32:41),test.errors.randomforest, type = "b", xlab ="number of feature", ylab ="RMSE")
# ```
# 
# ```{r}
# library(randomForest)
# set.seed(1)
# train.errors.randomforesttree = rep(0, 10)
# test.errors.randomforesttree  = rep(0, 10)
#  for (i in 1:10){
# rate.fit.randomforest = randomForest(Rating_install_target~., data = data.Train,mtry= 12,ntree =100 *i, importance=TRUE)
# train.errors.randomforesttree[i] = (mean((rate.fit.randomforest$predicted-rate.fit.randomforest$y)^2))^0.5
# data_ratehat = predict(rate.fit.randomforest, newdata = data[-train,])
# test.errors.randomforesttree[i] =  mean((data_ratehat-data.testX)^2)^0.5
# }
# ```
# random forest 
# ```{r}
# library(randomForest)
# set.seed(1)
# train.errors.randomforesttree = rep(0, 5)
# test.errors.randomforesttree  = rep(0, 5)
# for (i in 1:5){
# + rate.fit.randomforest = randomForest(Rating_install_target~., data = data.Train,mtry= 12,ntree =500 *i, importance=TRUE)
# + train.errors.randomforesttree[i] = (mean((rate.fit.randomforest$predicted-rate.fit.randomforest$y)^2))^0.5
# data_ratehat = predict(rate.fit.randomforest, newdata = data[-train,])
# test.errors.randomforesttree[i] =  mean((data_ratehat-data.testX)^2)^0.5
# }
# ```

